Language-Based Security for Low-Level MPC

### 2024-09-02 ppdp24/slides.tex
checkpoint

@@

\begin{frame}{The Ideal Functionality}
  A \emph{protocol} $\prog$ implements an \emph{ideal functionality} $\idealf$,
  defined in terms of operations in a prime field $\mathbb{F}_p$.
  \begin{itemize}
  \item The inputs are \cemph{secret values} of \cemph{clients} in a \emph{federation}
    $\setit{1,...,j}$.
  \item The \cemph{output} is made publicly available by $\prog$
  \end{itemize}
  The output may leak secret information to an \cemph{adversary} trying to
  guess secret values.  Consider:
  $$
  \idealf(x,y) = x * y
  $$
  If the output is odd, the adversary knows both secrets must be.  
\end{frame}

\begin{frame}{Protocol Implementation}

  Low-level, probabilistic protocols are defined in terms of basic variable types:
  \begin{itemize}
  \item $\secret{x}$: secret values in $\mathbb{F}_p$.
  \item $\mesg{x}$: messages received during the protocol.
  \item $\flip{x}$: uniformly random samples from $\mathbb{F}_p$ (implemented with
    a random tape semantics).
  \end{itemize}
  We can localize variables and expressions to \emph{clients}, and any information
  exchanged between clients must be through messaging.
  \begin{exampleblock}{Toy Example}
    $$
    \begin{array}{rcl@{\qquad}l}
      \mx{x}{1} &:=& \elab{(\secret{x} - \flip{x})}{2}  & \textit{(unicast)}\\
      \mx{y}{*} &:=& \elab{(\flip{y} + \mesg{x})}{1}  & \textit{(broadcast)}
    \end{array}
    $$ 
  \end{exampleblock}
\end{frame}

\begin{frame}{(Passive) Threat Model}
  The adversary wants to guess secrets. In addition to knowing the public
  output, the adversary may also corrupt some subset of clients $C$:
  \begin{itemize}
  \item adversary has access to the secrets of clients in $C$.
  \item adversary has access to messages received by members of $C$ during execution of $\prog$,
    aka \cemph{adversarial views}.
  \end{itemize}

@@

>>>>

\usepackage[style=verbose,backend=biber]{biblatex}
\addbibresource{secure-computation-bibliography.bib}

@@

\begin{frame}{The Ideal Functionality}
  A \emph{protocol} $\prog$ implements an \emph{ideal functionality} $\idealf$,
  defined in terms of operations in a prime field $\mathbb{F}_p$.
  \begin{itemize}
  \item The inputs are \cemph{secret values} of \cemph{clients} in a \emph{federation}
    $\setit{1,...,j}$.
  \item The \cemph{output} is made \emph{publicly available} by $\prog$
  \end{itemize}
  The output may leak secret information to an \cemph{adversary} trying to
  guess secret values.

  \begin{exampleblock}{Consider:}
  $$
  \idealf(x,y) = x * y
  $$
  If the output is odd, the adversary knows both $x$ and $y$ must be, even
  if $x$ and $y$ remain hidden.
  \end{exampleblock}

\begin{frame}{Protocol Implementation in Overture}

  Low-level, probabilistic protocols are defined in terms of basic variable types
  (identifiers $x$ distinguish them):
  \begin{itemize}
  \item $\secret{x}$: secret values in $\mathbb{F}_p$.
  \item $\mesg{x}$: messages received during the protocol.
  \item $\flip{x}$: uniformly random samples from $\mathbb{F}_p$ (implemented with
    a random tape semantics).
  \end{itemize}
  We can localize variables and expressions to \emph{clients}, and any information
  exchanged between clients must be through messaging.
  \begin{exampleblock}{Toy Example:}
    $$
    \begin{array}{rcl@{\qquad}l}
      \mx{x}{1} &:=& \elab{(\secret{x} - \flip{x})}{2}  & \textit{(unicast)}\\
      \mx{y}{*} &:=& \elab{(\flip{y} + \mesg{x})}{1}  & \textit{(broadcast)}
    \end{array}
    $$ 
  \end{exampleblock}
\end{frame}

\begin{frame}{(Passive) Threat Model}
  The adversary wants to guess secrets. In addition to knowing the public
  output, the adversary may also corrupt \emph{any} subset of clients $C$:
  \begin{itemize}
  \item adversary has access to the secrets of clients in $C$.
  \item adversary has access to messages received by members of $C$ during execution of $\prog$,
    aka \cemph{adversarial views}.
  \end{itemize}

@@

\section{Models of a Protocol}

\begin{frame}{Computing Protocol Distributions}

  The probability distribution of a protocol $\prog$ (as a pmf) can be precisely computed
  by interpretation as a \cemph{constraint program}.
  \begin{itemize}
  \item Interpretation as a Datalog program-- set of Least Herbrand Models.
    \begin{itemize}
      \item Random tapes represented as fact base.
    \end{itemize}
  \item Interpretation as SMT constraints \footnote{Ozdemir, A., Kremer, G., Tinelli, C., Barrett, C. (2023). \emph{Satisfiability Modulo Finite Fields}. In: Enea, C., Lal, A. (eds) Computer Aided Verification. CAV 2023. }-- set of all models.
  \end{itemize}
  Set of models can be queried to enforce hyperproperties-- but poor scaling.

  \begin{alertblock}{Hypothesis: Composable Properties}
    Compositional properties of protocol components can be independently verified, tractably.
  \end{alertblock}
